---
title: "Plotly examples"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Examples of plotly

We're gonna look at NYC Airbnb data.

# Loading data

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

```{r}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(rating = review_scores_location / 2) |>
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) |>
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500) 
```

 price %in% 100:500): price in the range of 100 to 500.
 
# Plotly plots
 
## scatterplot

```{r}
nyc_airbnb %>% 
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% 
  plot_ly(
    x = ~lat, y = ~long, color = ~price, text = ~text_label,
          alpha = .5,
          type = "scatter", mode = "markers")
```

plot_ly: graphing
mode = "markers": This displays each data point as a distinct marker.
mode = "lines": This connects the data points with lines.
mode = "lines+markers": This combines both lines and markers, showing the individual data points and connecting them with lines.
text =~rating: when you put mouse at one point, it will show x, y and rating.
text = ~text_label: show the text_label we defined

## boxplot

```{r}
nyc_airbnb  %>%  
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(
    y = ~price, x = ~ neighbourhood, color = ~neighbourhood, type = "box", colors = "viridis")
```

fct_reorder(neighbourhood, price): reorder neighbourhood according to price

## bar plot
```{r}
nyc_airbnb  %>%  
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(
    x = ~neighbourhood, y = ~n, color = ~neighbourhood, 
    type = "bar", colors = "viridis")
```

